Corrections to Manuscript No. 15-TIE-3480

### 2016-03-29 RMS/corrections.tex
modified version wrt Zhou Min's comments

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{{\bf ANSWER}}

@@

\begin{center}
  \begin{tabular}{r l}
    \hline\hline
    & \\
    Manuscript Number: & 15-TIE-3480\\
    Manuscript Title: & Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation\\
    & with Real-Time Maude \\
    Submitted to: & Transactions on Industrial Eletronics \\
    Manuscript Type: & Regular paper \\
    & \\
    \hline\hline
  \end{tabular}
  \bigskip
\end{center}

@@

\section{Answers to the Reviewers}
\subsection{Reviewer 1}
Comments to the Author

The paper shows a realistic implementation of a Rate-Monotonic
Scheduling algorithm using Real-Time Maude (a modeling language based
on rewriting logic) by taking into account the overhead of scheduling
and some other details of the hardware platform. The correctness of
the implementation with respect to the algorithm and the completeness
of the model are verified by model checking, and validated within
different realistic scenarios.

On the positive side, this paper presents a solid piece of
work. Periodic task scheduling is an important (and difficult)
problem, and the topic of the paper appears to be well suited within
the field of the industrial real-time systems. Overall the paper is
well structured, technically accurate, presents the work in a
comprehensive and reasonable way, and tackles theoretical as well as
practical aspects. There are two principal contributions of the paper:

@@

On the negative side:

1) The weak point is the lack of evidence of practicality, efficiency
and scalability. Since there are only small and simplistic scenarios
to analyze this model, it is difficult to judge the effectiveness of
the proposed implementation. The key scenarios appear conveniently
small to allow the implementation fully supports all these examples,
returning at the same time appropriate counterexamples to guide and
adjust the design. Is this true for larger examples of "real world"
applications within the field of industrial real-time systems? How do
the authors propose to handle very large scenarios? How does it behave
on typical real-time scheduling problems used in industry? I would
like to see more complex examples to convince the reader of the
practicability of the approach on the assumptions given for the model,
and would probably increase the mentioned benefits. The paper does not
give any directions to the above problems, and some sentences pointing
out the difficulties in the implementation of more generic and
realistic scenarios would be most welcome to understand the real
contribution of the paper.

\ANSWER: As mentioned in the paper, the modeled RMS implementation
serves in an avionic control systems from our industrial partner. It
is a real-world application within the field of industrial real-time
systems. And the scenarios presented in Section V.B are also real
scenarios that our partner is using in the system. Our partner
indicated that there would be at most $5$ tasks in the task set for
the implementation. On the other hand, in the current version, we have
randomly generated large numbers of test cases to examine the
efficiency of our schedulability test that is based on model checking,
as discussed in Section V.B. The capability of model checking is
restricted by the scale of the state space of the model. In our model,
the model checking can handle scenarios where $mn$ is up to $10^6$ in
an acceptable period of time. With $mn=10^6$ and reasonable task
periods, the number $n$ of tasks can be at least $10$, which has
already fulfilled the requirements of the target
implementation. Further with particular task periods, the number $n$
of tasks can be $20$ or more.

2) One of my biggest problems with the theoretical part of this work
is that the paper is technically solid as far as I can tell, but
there's not much yet in the way of theorems and results about formal
properties in Maude. The complete and detailed proof of the Theorem 2
should be provided somewhere. If the proof of the main results of
schedulability and correctness of the model is straightforward (as is
suggested) it seems not necessary to present a complex formalism on
Real-Time Maude and all the theorems provided are natural consequences
of Theorem 1. I agree that even non-surprising results need to be
investigated in the proof of Theorem 2, some sentences pointing out
the difficulties in the theoretical formalization in Real-Time Maude
would be most welcome. Please, include (e.g., in an appendix or even
in a technical report) a detailed proof.

\ANSWER: The detailed proof is now included in the Appendix. It is true
that readers may be interested in the detailed proof of Theorem~2 to
feel convinced of the completeness of our approach. However, the proof
needs a bit more theoretical background about rewriting logic and more
details of our model, which we have simplified in the submission to
ease the understanding of our approach. We would prefer to refer the
detailed proof to a non-anonymous technical report, if possible, in
the final version.

3) Another important point which needs improvement is the description
of the implementation. I guess other readers might have less
difficulties with the motivations if they know Maude and the Real-Time
Maude extension, but if you aim for a more general audience, it might
not work. Many pages are spent for the description of the formal
modeling of the implementation and the section is hard to read. I
highly recommend the authors to thoroughly revise this part of the
paper to make it easy-to-read. It would be better preferable to have a
much shorter description of the principal insights for the
implementation followed by more convincing examples and benchmarks
with respect to related work to convince the reader of the
practicability of the approach. You should try to summarize this
section and to extend the original contribution. From my point of
view, there is a trade off in this paper between the contributions and
the presentation of the implementation.

\ANSWER: Thank you for the invaluable suggestions. Section IV has been
revised. Some unnecessary detailed definitions presented as codes are
removed, and replaced by more explanations. We hope that the current
presentation would make Section IV more easy-to-read, even for an
audience who does not know Real-Time Maude before. On the other hand,
Section VI (Related Work) is also improved. We compare our work with
the existing theoretical work and the existing verification work in a
more complete way.

In conclusion, the RMS implementation proposed by the authors by using
Real-Time Maude is interesting, but not complete (theorems and results
about the formal modeling and verification of the implementation in
Maude ought be clearly demonstrated). Moreover, the weak point is the
lack of evidence for practicality, and the presentation of Section IV
can be improved. It's not clear at all how this kind of key scenarios
could actually run in practice in more general real-time
systems. However, I think that the paper is worthy of publication,
because is the first time that Rate-Monotonic Scheduling is
investigated using Real-Time Maude in a (more) realistic
implementation, providing a solid semantic foundation for formal
verification. Therefore, I recommend the (weak) acceptance of this
paper.

Some minor remarks:

- Page 7, Related Work. More comparisons with other approaches based
on model checking would help to evaluate pros and cons of an
implementation with Real-Time Maude with respect to different
languages and tools. The authors should review the comparison with
[24] and [25] more thoroughly. You should benchmark your approach
against others.

\ANSWER: The related work section is now improved. More comparisons
with the theoretical approaches and with [24,25] are added. The
differences with [24,25] in the models and in the way of modeling are
mainly discussed. On the other hand, it is a bit difficult to compare
the efficiency and scalability between [24,25] and our approach. One
reason is that we have a different setting with [24] and [25], because
the objectives are different: we aim at verifying an RMS implemention
from a real-world real-time system, while [24] and [25] targeted the
RMS algorithm itself. Another reason is that [24] and [25] presented
no discussion on the efficiency and scalability. Furthermore, they use
\verb|TMSVL| and an extension of SPIN, respectively, as verification
tools, which are not open-source, making it unable to re-implement
their work.

- Page 8, Conclusions. Where in the paper do you show that the details
of your "realistic" implementation are "sufficient" for the behaviors
of all real systems used in the current industry? This should be
briefly discussed.

\ANSWER: The statement has been corrected. The work presented in this
submission aims at modeling and verifying a realistic RMS
implementation in an industrial avonic system. It is a piece of real
work in the industry. Even though we believe that our approach could
be applied to other systems as well, it means more to that specific
one. In this sense, ``sufficient'' means that the details described in
our model meet the requirements and expectations from the users and
the engineers.

\subsection{Reviewer 2}
Comments to the Author

The paper proposes a new way of modelling Rate Monotonic Scheduling
(RMS).  The new modelling approach is more accurate than the
simplified way originally proposed by Liu and Layland, as it also
models some of the overhead that is present in a real system
(e.g. scheduling and switching time).  This implies taking some of the
hardware details into account.  The model, which is based on the
formal language of Real-Time Maude, can be analyzed using the formal
verification tools provided by Real-Time Maude.  The paper shows how
this approach can be used for modelling and analyzing a particular RMS
implementation.

Up to my knowledge, this is original work. Related papers address
different aspects and do not take implementation overhead into
account.

The technique proposed by the paper is of industrial interest because
it improves the accuracy of analyzing schedulability in RMS
implementations with respect to the bare application of the theoretic
schedulability result.

The paper is well written and it looks sound, but I could not check it
completely.

One of the problems with this paper is that it is not completely
self-contained.  Some knowledge about Real-Time Maude is necessary in
order to fully understand it.  I found the short introduction about
Real-Time Maude (section II.B) not enough for understanding the
formalism used in the rest of the paper (see details below).

\ANSWER: The Sections II.B and IV are improved to be more
self-contained now. The idea is that, Section II.B contains mainly an
overview of Real-Time Maude, and then Section IV describes the model
with introducing necessary syntax on-the-fly.

Another concern is that the significance of the paper could be much
better if the paper addressed the problem of modelling RMS in a more
general way. Instead, the paper takes the form of a case study, where
the formal modelling of one specific RMS implementation is presented,
rather than a general method for modelling and analyzing RMS
implementations.

\ANSWER: Yes, we agree that we have two choices to do the work
presented in the paper: one is to develop a general way to model RMS
algorithms or implementations, and then instantiate the general model
to get a concrete one for our target system; the other is to shape an
accurate model of the target system directly. To us, there is a trade
off between these two directions. We chose the latter with some
concerns. By our experience, the engineers, who write the codes, and
those, who are in charge of verifying the system or the codes, are
usually not the same persons. When a verification engineer models a
system, he is actually abstacting the system or the codes. It is
difficult to ensure that the model behaves the same as the system or
the codes.  And it is more difficult to let other engineers and users
believe that the model behaves the same as the system or the
codes. Furthermore, the developers and users hope that the model
behaves not only the same as what they had in mind, but also the same
as what is written in the codes. A way out is to make the model not
only behave like the codes, but also ``look'' like the codes. This
requires the model to be as accurate as possible. It makes the model
specific, but improves the engineers' confidence in the model and the
verification results. That is also why we emphasize the
correspondences between the functions in the model and the lines in
the pseudocode, when we introduce our model in Section~IV. On the
other hand, we are also interested in the first choice. This will be
the future work and we would try to get a better balance between them.

Also, the discussion about soundness and
completeness of the analysis (section V.C) is not fully developed and,
once again, it refers to the specific model rather than being a
general result.

\ANSWER: The section about soundness and completeness is now made more
self-contained. The detailed proof of Theorem~2 is included in the
appendix. On the other hand, since we chose the accurate way to
achieve the model as discussed above, yes, the proof is a specific
one.

As a conclusion, even if the significance of the paper is not as much
as it could be, I think the paper provides something novel and
interesting for the readers. Hence, my recommendation is to accept
this paper provided it is made more self-contained (without assuming
any reader's knowledge about Maude) and the proof of completeness and
soundness is fully developed.

Detailed comments
\begin{itemize}
\item
Section II.B

- In the definition of $IR$, it is not clear what $s$ and $s'$ are. I
guess they are states, but the concept of state was not introduced.

\ANSWER: Yes, they can be states. But more generally, they are
terms. This part has been modified to specify $s$ and $s'$ ($t$ and
$t'$ now) clearly.

- In the definition of a class, the authors should specify that a
class includes a collection of rules, otherwise this fact may be
missed.

\ANSWER: Thanks very much for reminding. This is added now.

\item
Section III

- Page 2 right column, line -24: The implementation is shown as
schedule() in Figure 1 $\rightarrow$ The pseudocode of schedule() is
shown in Figure 1

\ANSWER: It is done.

\item
Section IV.A

- I don't understand the meaning of [ctor] in the definition of some
operations (maybe because I have no specific background on Maude). I
could not find the explanation of this writing in the introduction to
Maude.

\ANSWER: Sorry for missing the explanation of \verb|[ctor]|. It is now
added when \verb|[ctor]| is used for the first time.

- For the stack sort, the authors mention operations push, pop and
peek, but then you don't write the definitions of these
operations. Instead, they write the definitions of bottom and \#,
which are not explained in the text. This part should be made clearer.

\ANSWER: Sorry for the misleading in the text. In fact, \verb|bottom|
and \verb|#| are constructors of sort \verb|Stack|. This part is
modified now. Some detailed definitions in codes are removed, and are
replaced by more explanations. We hope that the current presentation
would make Section IV more easy-to-read.

- Also, the meaning of NzNat is not explained.

\ANSWER: Sorry for this incompleteness. \verb|NzNat| did mean non-zero
natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
unnecessary complexity for the readers.

\item
Section V.C

- In the statement of theorem 1, the definition of time-robust
real-time rewrite theory is missing. Also, the meaning of
tick-stabilizing atomic propositions is not defined. This makes the
section not self-contained.

\ANSWER: In fact, the definitions of time-robustness and
tick-stabilization (which is now replaced with tick-invariance)
require more knowledge about rewriting logic. We avoid introducing the
accurate definitions of them. Instead, we now give short descriptions
of them. More detailed introduction can be found in the Appendix.

- The proof of theorem 2 is missing. The authors just indicate how the
proof could be developed, but they do not develop it. A possibility
would be to point to a document where this proof has been developed.

\ANSWER: The detailed proof is now included in the appendix.  The
detailed proof requires a bit more theoretical background about
rewriting logic and more details of our model, which we tried to
simplify in the submission to ease the understanding of our
approach. We would prefer to refer the detailed proof to a
non-anonymous technical report, if possible, in the final version.
\end{itemize}

\subsection{Reviewer 3}
Comments to the Author

This paper stuides the implementation of a rate-monotonic scheduling
with real-time maude, according to my carefully reading of this paper,
I do not think this paper is qualified for TIE due to the following
reasons:

1. Rate-monotonic scheduling is a very simple scheduling and has been
sufficiently investigated in the field of embedded system, the authors
claim the innovation of this paper as the implementation using
real-time maude, however, I cannot see any special point (or
advantage) when using this real-time maude in modelling RMS.

\ANSWER: We agree that RMS is a very simple scheduling and is the
optimum at the same time among the fixed-prority ones, making it
widely applied and sufficiently investigated. Besides the ideal
setting, the schedulability of RMS was also investigated under
different kinds of implementations with consideration about overhead,
as we discuss in the related work section (Section VI). Despite the
reason that the existing results do not fit our target system using
RMS, the most important motivation to develop the work presented is
that, we aim at verifying the system not only for the schedulability,
but also for the correctness. That is, we want to verify that the
target system does schedule the tasks under the RMS algorithm. The
work presented should be seen as a verification problem, instead of a
schedulability test.

2. RMS has many different realization methods, no comparison is given
to justify the strong point of real-time maude when applied to RMS.

\ANSWER: The comparison is given in the related work section (Section
VI). We would say that we are not implementing RMS algorithm in
Real-Time Maude. In fact, we are using Real-Time Maude to model an
realistic implementation of RMS from an industrial avionic
system. There is no theoretical reason telling us that we have to use
Real-Time Maude to model the RMS implementation. However, the existing
verification work as far as we know cannot fit our needs, as discussed
in Section VI. Therefore, we developed the work in the paper, as a
piece of real work in the industry.

3. The assumptions given in IV is too rigid, which makes the
scheduling problem to be investigated by very simple, then what is the
difficulty?

\ANSWER: As an industrial application, we are not trying to make the
problem as difficult as possible. Instead, we are trying to simplify
the model so that the existing tools are able to solve, while the
target system satisfies the assumptions on the model so that the
verification results are trustworthy. On the other hand, the
assumptions are not so rigid. For example, the mask mechanism
considered as hardware details makes the job initiation times of task
$\tau_i$ possibly not equal to $kT_i$, implying that the deadlines of
the jobs may be not equal to $(k+1)T_i$ (see assumption A1'). Another
example is that non-determinism exists in our model, as discussed in
Section VI.

4. The description in section IV (A-E) is trivial, it can only be
viewed as a simple application of the rewriting logic.

\ANSWER: Yes, we agree that this is an application of rewriting
logic. In this paper, we do apply the existing theories and techniques
of rewriting logic to solve a real industrial problem, which has not
yet been investigated by this sort of techniques, achieving an
industrial contribution.

5. The model checking part is not sufficiently discussed, the authors
only list the commands but not illustrate the mechanism behind these
commands.

\ANSWER: We do not agree that we should illustrate the mechanism behind
the model checking commands, since the model checker is not part of
our contributions in the paper.

Based on the above comments, I thinks this paper is only a simple
application [26] and [27] in RMS, hence I do not recommend this paper.

>>>>

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{{\bf RESPONSE: }}
\newcommand{\COMMENT}{{\bf COMMENT: }}

@@

\begin{center}
  \begin{tabular}{r l}
    \hline\hline
    & \\
    Manuscript Number: & 15-TIE-3480\\
    Manuscript Title: & Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation\\
    & with Real-Time Maude \\
    Submitted to: & Transactions on Industrial Electronics \\
    Manuscript Type: & Regular paper \\
    & \\
    \hline\hline
  \end{tabular}
  \bigskip
\end{center}

@@

%\section{Answers to the Reviewers}
\section{Reponses to Reviewer 1}
\subsection{General Comments}
\begin{itemize}

\item
\hide{
The paper shows a realistic implementation of a Rate-Monotonic
Scheduling algorithm using Real-Time Maude (a modeling language based
on rewriting logic) by taking into account the overhead of scheduling
and some other details of the hardware platform. The correctness of
the implementation with respect to the algorithm and the completeness
of the model are verified by model checking, and validated within
different realistic scenarios.}
\COMMENT On the positive side, this paper presents a solid piece of
work. Periodic task scheduling is an important (and difficult)
problem, and the topic of the paper appears to be well suited within
the field of the industrial real-time systems. Overall the paper is
well structured, technically accurate, presents the work in a
comprehensive and reasonable way, and tackles theoretical as well as
practical aspects. There are two principal contributions of the paper:

@@

\ANSWER Thanks for the pros. We are happy that the work in the paper
interests the readers. We hope that it provides a new and formal way
to verify a real-time system, which is able to investigate important
problems (such as periodic task scheduling) from a more realistic
aspect.

\item
\COMMENT The weak point is the lack of evidence of practicality,
efficiency and scalability. Since there are only small and simplistic
scenarios to analyze this model, it is difficult to judge the
effectiveness of the proposed implementation. The key scenarios appear
conveniently small to allow the implementation fully supports all
these examples, returning at the same time appropriate counterexamples
to guide and adjust the design. Is this true for larger examples of
"real world" applications within the field of industrial real-time
systems? How do the authors propose to handle very large scenarios?
How does it behave on typical real-time scheduling problems used in
industry? I would like to see more complex examples to convince the
reader of the practicability of the approach on the assumptions given
for the model, and would probably increase the mentioned benefits. The
paper does not give any directions to the above problems, and some
sentences pointing out the difficulties in the implementation of more
generic and realistic scenarios would be most welcome to understand
the real contribution of the paper.

\ANSWER Thanks for the suggestion. As mentioned in the paper, the
system under verification is a real-world RMS implementation, which is
used in an avionic control system. The scenarios presented in Section
V.B are also real scenarios from the online system. Our industrial
partner has very strict requirements in the timing. They use at most
$5$ tasks for scheduling to avoid high overhead.

On the other hand, ``larger'' scenarios are not the same as
``complex'' scenarios in our model, as discussed in the revised
Section V.B. We have examined our approach by verifying randomly
generated scenarios where the number $n$ of tasks are over $10$. In
that case, the least common multiple of the periods of all tasks can
be as large as $10^5$ times the interrupt cycle $T$. All feasible
combinations of execution traces are checked in our approach. Our
industrial partner agrees that it satisfies their practical
requirements. Furthermore, the number $n$ of tasks can be $20$ and
even more if we allow different tasks possess a same period.

\hide{
the modeled RMS implementation serves in an avionic control systems
from our industrial partner. It is a real-world application within the
field of industrial real-time systems. And the scenarios presented in
Section V.B are also real scenarios that our partner is using in the
system. Our partner indicated that there would be at most $5$ tasks in
the task set for the implementation. On the other hand, in the current
version, we have randomly generated large numbers of test cases to
examine the efficiency of our schedulability test that is based on
model checking, as discussed in Section V.B. The capability of model
checking is restricted by the scale of the state space of the
model. In our model, the model checking can handle scenarios where
$mn$ is up to $10^6$ in an acceptable period of time. With $mn=10^6$
and reasonable task periods, the number $n$ of tasks can be at least
$10$, which has already fulfilled the requirements of the target
implementation. Further with particular task periods, the number $n$
of tasks can be $20$ or more.
}

\item
\COMMENT One of my biggest problems with the theoretical part of this
work is that the paper is technically solid as far as I can tell, but
there's not much yet in the way of theorems and results about formal
properties in Maude. The complete and detailed proof of the Theorem 2
should be provided somewhere. If the proof of the main results of
schedulability and correctness of the model is straightforward (as is
suggested) it seems not necessary to present a complex formalism on
Real-Time Maude and all the theorems provided are natural consequences
of Theorem 1. I agree that even non-surprising results need to be
investigated in the proof of Theorem 2, some sentences pointing out
the difficulties in the theoretical formalization in Real-Time Maude
would be most welcome. Please, include (e.g., in an appendix or even
in a technical report) a detailed proof.

\ANSWER We are happy that the readers are interested in the detailed
and technical proof, which is now included in the Appendix. It is true
that readers may be interested in the detailed proof of Theorem~2 to
feel convinced of the completeness of our approach. However, the proof
needs a bit more theoretical background about rewriting logic and more
technical details of our model, which we have simplified in the paper
in order to ease the understanding of our approach. We would prefer to
refer the detailed proof to a non-anonymous technical report, if
possible, in the final version.

\item
\COMMENT Another important point which needs improvement is the
description of the implementation. I guess other readers might have
less difficulties with the motivations if they know Maude and the
Real-Time Maude extension, but if you aim for a more general audience,
it might not work. Many pages are spent for the description of the
formal modeling of the implementation and the section is hard to
read. I highly recommend the authors to thoroughly revise this part of
the paper to make it easy-to-read. It would be better preferable to
have a much shorter description of the principal insights for the
implementation followed by more convincing examples and benchmarks
with respect to related work to convince the reader of the
practicability of the approach. You should try to summarize this
section and to extend the original contribution. From my point of
view, there is a trade off in this paper between the contributions and
the presentation of the implementation.

\ANSWER Thank you for the invaluable suggestions. Section IV has been
revised. Some unnecessary detailed definitions presented as code are
removed, and replaced by more explanations. We hope that the current
presentation would make Section IV more easy-to-read, even for an
audience who did not know Real-Time Maude before. On the other hand,
Section VI (Related Work) is also improved. We compare our work with
the existing theoretical work and the existing verification work in a
more complete way.

\end{itemize}

\subsection{Detailed Comments}
\begin{itemize}
\item
\COMMENT Page 7, Related Work. More comparisons with other approaches
based on model checking would help to evaluate pros and cons of an
implementation with Real-Time Maude with respect to different
languages and tools. The authors should review the comparison with
[24] and [25] more thoroughly. You should benchmark your approach
against others.

\ANSWER Thanks for the pointing this out. The related work section is
now improved. More comparisons with the theoretical approaches and
with [24,25] are added. The differences with [24,25] in the models and
in the way of modeling are mainly discussed. On the other hand, it is
a bit difficult to compare the efficiency and scalability between
[24,25] and our approach. One reason is that we have a different
setting with [24] and [25], because the objectives are different: we
aim at verifying an RMS implemention from a real-world real-time
system, while [24] and [25] targeted the RMS algorithm itself. Another
reason is that [24] and [25] presented no discussion on the efficiency
and scalability. Furthermore, they used \verb|TMSVL| and an extension
of SPIN, respectively, as verification tools, which are not
open-source, making us unable to re-implement their work.

\item
\COMMENT Page 8, Conclusions. Where in the paper do you show that the
details of your "realistic" implementation are "sufficient" for the
behaviors of all real systems used in the current industry? This
should be briefly discussed.

\ANSWER Sorry for that. The statement has been corrected. The work
presented in the paper aims at modeling and verifying a realistic RMS
implementation in an industrial avionic system. It is a piece of real
work in the industry. Even though we believe that our approach could
be applied to other similar systems as well, it means more to that
specific one. In this sense, ``sufficient'' means that the details
described in our model meet the requirements and expectations from the
users and the engineers.

\end{itemize}

\section{Responses to Reviewer 2}
\subsection{General Comments}
\begin{itemize}
\item
\COMMENT One of the problems with this paper is that it is not
completely self-contained.  Some knowledge about Real-Time Maude is
necessary in order to fully understand it.  I found the short
introduction about Real-Time Maude (section II.B) not enough for
understanding the formalism used in the rest of the paper (see details
below).

\ANSWER Thank you very much for pointing this out. The Sections II.B
and IV are improved to be more self-contained now. The idea is that,
Section II.B presents mainly an overview of Real-Time Maude, and then
Section IV describes the model with introducing necessary syntax
on-the-fly.

\item
\COMMENT Another concern is that the significance of the paper could
be much better if the paper addressed the problem of modelling RMS in
a more general way. Instead, the paper takes the form of a case study,
where the formal modelling of one specific RMS implementation is
presented, rather than a general method for modelling and analyzing
RMS implementations.

\ANSWER Thank you for the suggestion. Yes, we agree that we have two
choices to do the work presented in the paper: one is to develop a
general way to model RMS algorithms or implementations, and then
instantiate the general model to get a concrete one for our target
system; the other is to shape an accurate model of the target system
directly.

To us, there is a trade off between these two directions. We did
choose the latter according to the following considerations. By our
experience, \emph{the development engineers (who write the code) and
  verification engineers (who verify the code or the system) are
  usually not the same persons.} When a verification engineer models a
system, he is actually abstacting the system or the codes. It is
difficult to ensure that the model behaves the same as the system or
the codes.  And it is more difficult to make other engineers and users
believe that the model behaves the same as the system or the
codes. Furthermore, the developers and users hope that the model
behaves not only the same as what they had in mind, but also the same
as what is written in the code. A way out is to make the model not
only \emph{behave like} the code, but also \emph{``look'' like} the
code. This requires the model to be as accurate as possible, based on
a fact that the expressivity of the modeling language is powerful
enough. It makes the model specific, but improves the engineers'
confidence in the model and the verification results. That is also why
we emphasize the correspondences between the functions in the model
and the lines in the pseudocode, when we introduce our model in
Section~IV.

On the other hand, we are also interested in the first direction. This
will be the future work and we would try to get a better balance
between them.

\item
\COMMENT Also, the discussion about soundness and completeness of the
analysis (section V.C) is not fully developed and, once again, it
refers to the specific model rather than being a general result.

\ANSWER Thanks for this comment. The section about soundness and
completeness is now made more self-contained. The detailed proof of
Theorem~2 is included in the Appendix. On the other hand, since we
chose the accurate way to achieve the model as discussed above, yes,
the proof is a specific one.

\end{itemize}

\subsection{Detailed Comments}
\begin{itemize}
\item
\COMMENT [Section II.B] In the definition of $IR$, it is not clear
what $s$ and $s'$ are. I guess they are states, but the concept of
state was not introduced.

\ANSWER Yes, they can be states. But more generally, they are
terms. This part has been modified to specify $s$ and $s'$ (in fact,
$t$ and $t'$ now) clearly.

\item 
\COMMENT [Section II.B] In the definition of a class, the authors
should specify that a class includes a collection of rules, otherwise
this fact may be missed.

\ANSWER Thanks very much for reminding. This is added now.

\item
\COMMENT [Section III] Page 2 right column, line -24: The
implementation is shown as schedule() in Figure 1 $\rightarrow$ The
pseudocode of schedule() is shown in Figure 1

\ANSWER Thanks for the careful reading. It is done now.

\item 
\COMMENT [Section IV.A] I don't understand the meaning of
\verb|[ctor]| in the definition of some operations (maybe because I
have no specific background on Maude). I could not find the
explanation of this writing in the introduction to Maude.

\ANSWER Sorry for missing the explanation of \verb|[ctor]|. It is now
added when \verb|[ctor]| is used for the first time.

\item
\COMMENT [Section IV.A] For the stack sort, the authors mention
operations push, pop and peek, but then you don't write the
definitions of these operations. Instead, they write the definitions
of bottom and \#, which are not explained in the text. This part
should be made clearer.

\ANSWER Sorry for the misleading in the text. In fact, \verb|bottom|
and \verb|#| are constructors of sort \verb|Stack|. This part is
modified now. Some detailed definitions in code are removed, and are
replaced by more explanations. We hope that the current presentation
would make Section IV more easy-to-read.

\item
\COMMENT [Section IV.A] Also, the meaning of NzNat is not explained.

\ANSWER Sorry for this incompleteness. \verb|NzNat| did mean non-zero
natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
unnecessary complexity for the readers.

\item
\COMMENT [Section V.C] In the statement of Theorem~1, the definition
of time-robust real-time rewrite theory is missing. Also, the meaning
of tick-stabilizing atomic propositions is not defined. This makes the
section not self-contained.

\ANSWER Sorry for the inconvenience for reading. In fact, the
definitions of time-robustness and tick-stabilization (which is now
replaced with tick-invariance) require more knowledge about rewriting
logic. We avoid introducing the accurate definitions of them. Instead,
now we give short descriptions of them before Theorem~1. More detailed
introduction can be found in the Appendix.

\item
\COMMENT [Section V.C] The proof of theorem 2 is missing. The authors
just indicate how the proof could be developed, but they do not
develop it. A possibility would be to point to a document where this
proof has been developed.

\ANSWER We are very happy that the readers are interested in the
detailed and technical proof, which is now included in the Appendix.
The detailed proof requires a bit more theoretical background about
rewriting logic and more details of our model, which we tried to
simplify in the paper in order to ease the understanding of our
approach. We would prefer to refer the detailed proof to a
non-anonymous technical report, if possible, in the final version.
\end{itemize}

\section{Responses to Reviewer 3}
\begin{itemize}
\item
\COMMENT RMS has many different realization methods, no comparison is
given to justify the strong point of real-time maude when applied to
RMS.

\ANSWER The comparison could be found in Section VI (and we have
expanded according to the reviewers' comments :-)). We would like to
clarify that we are \emph{not implementing} RMS, we are
\emph{verifying} it. We choose Real-Time Maude since it verifies the
model using model checking technique. If verification passes, no
deadline will be missed in the implementation as long as the model
assumptions are met.

\hide{
The comparison is given in the related work section (Section
VI). We would say that we are not implementing RMS algorithm in
Real-Time Maude. In fact, we are using Real-Time Maude to model an
realistic implementation of RMS from an industrial avionic
system. There is no theoretical reason telling us that we have to use
Real-Time Maude to model the RMS implementation. However, the existing
verification work as far as we know cannot fit our needs, as discussed
in Section VI. Therefore, we developed the work in the paper, as a
piece of real work in the industry.
}

\item
\COMMENT Rate-monotonic scheduling is a very simple scheduling and has
been sufficiently investigated in the field of embedded system, the
authors claim the innovation of this paper as the implementation using
real-time maude, however, I cannot see any special point (or
advantage) when using this real-time maude in modelling RMS.

\ANSWER Thank you for the insightful comment. We agree that RMS has
been intensively studied, because of its importance. However, most of
the results are based on the assumption that \emph{task switching does
  not take time}. That assumption is not realistic. Models with and
without the assumption have totally different behaviors. For instance,
as shown in Figure~2(b), in the RMS implementation we verified, the
switching from time $9$ to $11$ blocks the interrupt handling, hence
delaying the initiation time of $\tau_1$. To our knowledge, this kind
of phenomenon would not happen in the theoretical analysis
models. Although there is very few results that take into account the
switching overhead (as discussed in Section VI), none of them is
generic and our system under verification is not in their scope.

Despite the above reason, the most important motivation of this paper
is to verify the system not only for the schedulability, but also for
the correctness. That is, we want to verify that the target system
does schedule the tasks under the RMS algorithm. The work presented
should be seen as a verification problem, instead of a schedulability
test. From verification point of view, this paper models a real-world
RMS implementation with sufficient technical details. Two important
properties--schedulability and correctness--are verified by model
checking technique, and the soundness and completeness of the results
are demonstrated.

\hide{
is a very simple scheduling and is the optimum at the same time among
the fixed-prority ones, making it widely applied and sufficiently
investigated. Besides the ideal setting, the schedulability of RMS was
also investigated under different kinds of implementations with
consideration about overhead, as we discuss in the related work
section (Section VI). Despite the reason that the existing results do
not fit our target system using RMS, the most important motivation to
develop the work presented is that, we aim at verifying the system not
only for the schedulability, but also for the correctness. That is, we
want to verify that the target system does schedule the tasks under
the RMS algorithm. The work presented should be seen as a verification
problem, instead of a schedulability test.
}

\item
\COMMENT The assumptions given in IV is too rigid, which makes the
scheduling problem to be investigated by very simple, then what is the
difficulty?

\ANSWER Thank you for the question. When an automatic formal
verification tool (such as model checker) is used to verify a given
system, it explores the whole system state space to check whether the
given property holds. Then the state space explosion is the most
common problem for an automatic verification tool. That means the
state space of the system/model is too huge for the tool to explore
with acceptable temporal and spatial cost. The scale of the state
space depends on the complexity of the model of the system.

As an industrial verification application, we are not trying to make
the problem as difficult as possible. Instead, we are trying to
simplify the model so that the existing tools are able to solve, while
the target system satisfies the assumptions on the model so that the
verification results are trustworthy.

On the other hand, the assumptions are not so rigid. For example, the
mask mechanism considered makes the job initiation times of task
$\tau_i$ possibly not equal $kT_i$, implying that the deadlines of the
jobs may be not equal to $(k+1)T_i$ (see assumption A1'). This is also
discussed in the beginning of Section IV, pointing out the blocking at
time $10$ in Figure~2(b). Another example is that non-determinism
exists in our model, as discussed in Section~VI.

\item
\COMMENT The description in section IV (A-E) is trivial, it can only
be viewed as a simple application of the rewriting logic.

\ANSWER Thanks for the careful reading. We agree that this is an
application of rewriting logic. In this paper, we do apply the
existing theories and techniques of rewriting logic to solve a real
industrial problem, which has not yet been investigated by this sort
of techniques, achieving an industrial contribution.

\item
\COMMENT The model checking part is not sufficiently discussed, the
authors only list the commands but not illustrate the mechanism behind
these commands.

\ANSWER Thank you for the suggestion. However, since the model checker
is not part of our contributions in the paper, we do not think it is
appropriate to illustrate the mechanism behind the model checking
commands, which may confuse the readers on the other hand.

\end{itemize}
